Statically Typed String Sanitation Inside a Python

### 2014-08-13 sanitation-psp14/sanitation-psp14-short.tex
Cleaned up grammar of target language.

\inferrule[Tr-string]
{ \ }
{\trden{\strin{s}} = \tstr{s}}

\inferrule[Tr-Concat]
{ \trden{e_1} = \iota_1 \\ \trden{e_2} = \iota_2}
{\trden{\rsconcat{e_1}{e_2}} = \tconcat{\iota_1}{\iota_2}}

\inferrule[Tr-Subst]
{ \trden{e_1} = \iota_1 \\ \trden{e_2} = \iota_2 }
{\trden{ \sisubst{r}{e_1}{e_2} } = \tsubst{\rx{r}}{\iota_1}{\iota_2} }

\inferrule[Tr-Coerce-Ok]
{ e : \strin{r} \\ \lang{r'} \subseteq \lang{r}}
{\trden{ \coerce{r'}{e} } = \tstr{s}}

\inferrule[Tr-Coerce-NotOk]
{\trden{e} = \iota \\ e : \strin{r} \\ \lang{r'} \not \subseteq \lang{r}}
{\trden{\coerce{r'}{e}} = \tcheck{\rx{r'}}{\iota}}

\end{mathpar}
\caption{Translation from source terms (S) to target terms (P).
The translation is type-directed in the Tr-Coerce cases.}
\end{figure*}
\addtocounter{figure}{-5}

@@

<P> ::= $\lambda x . e$ \hfill target terms \alt
  $e e$ \alt
  $\tstr{s}$ \alt
  $\rx{r}$ \alt
  $\tconcat{P}{P}$ \alt
  $\preplace{P}{P}{P}$ \alt
  $\tcheck{P}{P}$ 
  \end{grammar}
\caption{Syntax for the fragment of our target language, $\lambdap$, containing strings and statically constructed regular expressions.}
\label{fig:lcsSyntax}
\end{figure}

>>>>

\inferrule[Tr-Abs?]
{ \sctx \vdash \trden{e} = \iota }
{\sctx \vdash \trden{ \lambda x.e } = \lambda x . \iota}

\inferrule[Tr-App]
{\sctx \vdash \trden{e_1} = \iota_1 \\ \sctx \vdash \trden{e_2} = \iota_2}
{\sctx \vdash \trden{e_1e_2} = \iota_1\iota_2}

\inferrule[Tr-string]
{ \ }
{ \sctx \vdash  \trden{\strin{s}} = \tstr{s}}

\inferrule[Tr-Concat]
{ \sctx \vdash \trden{e_1} = \iota_1 \\ \sctx \vdash htrden{e_2} = \iota_2}
{ \sctx \vdash \trden{\rsconcat{e_1}{e_2}} = \tconcat{\iota_1}{\iota_2} }

\inferrule[Tr-Subst]
{ \sctx \vdash  \trden{e_1} = \iota_1 \\ \sctx \vdash  \trden{e_2} = \iota_2 }
{ \sctx \vdash  \trden{ \sisubst{r}{e_1}{e_2} } = \tsubst{\rx{r}}{\iota_1}{\iota_2} }

\inferrule[Tr-SafeCoerce]
{ \ }
{ \sctx \vdash  \trden{ \coerce{r'}{e} } = \trden{e} }

\inferrule[Tr-Check-Ok]
{ \sctx \vdash e : \stringin{r} \\ \lang{r} \subseteq \lang{r'} } 
{ \sctx \vdash  \trden{ \rcheck{r'}{e}{x.e_1}{e_2} } = \trden{[e/x]e_1} }

\inferrule[Tr-Check-NotOk]
{ \sctx \vdash e : \stringin{r} \\ \lang{r} \not \subseteq \lang{r'}}
{ \sctx \vdash  \trden{ \rcheck{r'}{e}{x.e_1}{e_2} } = \trden{\tcheck{r'}{e_2}} }

\end{mathpar}
\caption{Translation from source terms ($e$) to target terms ($\iota$).
The translation is type-directed in the Tr-SafeCoerce case.}
\end{figure*}
\addtocounter{figure}{-5}

@@

<P> ::= $\lambda x . \iota$ \hfill target terms \alt
  $\iota \iota$ \alt
  $\tstr{s}$ \alt
  $\rx{r}$ \alt
  $\tconcat{\iota}{\iota}$ \alt
  $\preplace{\iota}{\iota}{\iota}$ \alt
  $\tcheck{\iota}{\iota}$ 
  \end{grammar}
\caption{Syntax for the target language, $\lambdap$, containing strings and statically constructed regular expressions.}
\label{fig:lcsSyntax}
\end{figure}
